Forecasting the United States 2024 Presidential Election

### 2024-11-04 paper/paper.qmd
finished section on ideal poll questions design

- questions (wording, order, options)
- treatment of non-response
- offer of incentive

After analysis of poll responses, the votes of the consistent states should be added back into consideration before making the final forecast for election results.

>>>>

The wording of questions should be straightforward and easy to understand, minimizing error in measurement caused by misinterpretation of questions. The question should also be asked neutrally, without leading participants to any particular response. Likert scales, including an option for “don’t know”, should be used for all questions for ease and consistency of participant understanding. As well, keeping questions and answer options simple minimizes the burden placed on participants, which reduces the attrition caused by participants losing interest in the poll [@citeTB]. The “don’t know” option is also effective in helping reduce the decision difficulty to certain participants who are truly unsure. Before officially deploying the survey with our selected sample, it first needs to be tested to catch ambiguous or other poorly phrased questions [@citeTB]. To encourage participation in this research, a financial incentive should be offered for full completion of the poll.

After analysis of poll responses, the votes of the historically consistent states should be added back into consideration before making the final forecast for election results.
